% Section 1: Introduction (about 1 page). Plan: PAPER_PLAN 4 / §1.
%   p1 hook (LBSN, anticipate the next move, mobility-aware motivation).
%   p2 the two tasks (next-category, next-region; we do NOT predict the exact next place).
%   p3 the tension (sharing is not free; where it helps, where it costs).
%   p4 what we do (check-in-level representation + one model, two tasks).
%   p5 contributions (three bullets, stated positively).
%   p6 roadmap.
% Reminder: next-category / next-region; American English; no em-dash.
\section{Introduction}
\label{sec:intro}

Location-based social networks, such as Gowalla~\cite{cho2011gowalla},
let people share the places they visit. Each check-in is a small record of human
movement, and together these records show how people move through a city. A
natural and useful question is what a person will do next, because a service
that can anticipate the next move can prepare ahead of time instead of reacting
after the fact. For a mobility-aware service this can mean staging the right
content in the area a user is heading to, or planning capacity there before
demand arrives, and the same signal also helps recommendation and urban
analysis.

Predicting the next place exactly, a single point of interest (POI), is hard, and
it is often more than a service needs. Two coarser (less detailed) questions are
easier to answer and usually enough: the next category, the kind of place such as
food or shopping, and the next region, the part of the city a user is heading to
(a neighborhood-scale unit, the census tract in the U.S. and the \emph{mahalle}
in Istanbul). These two questions pair naturally, one for intent and one for
geography, and they are easier to predict accurately than a single POI while
still being useful. The question we study is whether one model should learn both
at once.

Sharing one representation across tasks is not free. Joint training can help one
task while hurting the other, a well-known trade-off in multi-task learning
(MTL), where one model does several jobs at once by sharing most of its parts and
the shared parameters settle on a compromise that suits neither task
perfectly~\cite{caruana1997multitask}; our earlier work~\cite{silva2025mtlnet}
observed exactly this for next-category and next-region. So the useful question is
not whether MTL is good in general, but where sharing helps, where it costs, and
how to share so the gains hold and the cost stays small.

We introduce two changes and measure each one carefully. First, we build a
check-in-level representation: instead of one fixed vector per place, where two
visits to the same coffee shop look identical, each check-in gets its own vector
that carries its context (the time, the nearby places, and the recent trail).
This extends hierarchical graph representations of places~\cite{huang2023hgi},
and the infomax idea behind them~\cite{velickovic2019dgi}, by adding a fourth,
check-in level beneath the place, region, and city levels
(Fig.~\ref{fig:dataflow}). Per-visit context is not new on its own; what is new
is obtaining it from inside this hierarchical graph representation, a choice we
test directly (Section~\ref{sec:related}). Second, we train one model that
predicts the next category and the next region in a single forward pass, with a
shared trunk that carries the semantic context and a private spatial path for the
region task (Fig.~\ref{fig:model}). We evaluate on two very different settings on purpose,
five U.S. states of different sizes (Gowalla) and one international city
(Istanbul), so we can see whether the findings hold across small and large, U.S.
and non-U.S. data.

Our contributions are the following.
\begin{itemize}
  \item A check-in-level representation that extends hierarchical graph infomax
    from the place to the individual visit. It improves next-category
    prediction by a large and consistent margin over a standard place embedding,
    about $+28$ to $+40$ points of macro-F1 (a balanced score that counts every
    category equally) across all five states, and a controlled test shows the
    gain comes from the per-visit context, not from extra supervision
    (Table~\ref{tab:substrate}); the margin is large because a single fixed vector
    per place cannot separate places that host several kinds of activity, which
    per-visit context recovers.
  \item A single model for joint next-category and next-region prediction that
    shares a semantic context across the two tasks while keeping a private path
    for the spatial one. In one forward pass it outperforms a dedicated
    single-task category model at every state (by about $+4.7$ to $+7.7$ points of
    macro-F1) and, on region, does so where there are many regions while staying
    statistically non-inferior within a two-point margin (TOST, a test of
    equivalence) where there are few (Table~\ref{tab:results}).
  \item An empirical account, across five states of different sizes and one
    international city, of how the joint gain scales with the number of regions.
    The category gain holds everywhere, and the region result moves monotonically:
    from a non-inferior match (TOST, $\pm2$ percentage points, or pp) at the small
    region counts to outperforming the dedicated model at the large, with the largest
    state (California) showing the largest region gain (Fig.~\ref{fig:deltas}).
    The joint results on the Gowalla states are measured over five folds at a
    single seed.
\end{itemize}

The rest of the paper reviews background and related work
(Section~\ref{sec:related}), defines the problem and the two tasks
(Section~\ref{sec:problem}), presents our method (Section~\ref{sec:method}) and
experimental setup (Section~\ref{sec:setup}), reports results
(Section~\ref{sec:results}), discusses findings and limitations
(Section~\ref{sec:discussion}), and concludes (Section~\ref{sec:conclusion}).
