% Section 2: Background and Related Work (about 1.0 page). Plan: PAPER_PLAN 4 / §2.
%   2.1 From place embeddings to per-visit embeddings (DGI -> HGI -> Check2HGI; CTLE contrast). Fig. \ref{fig:dataflow}.
%   2.2 Predicting the next category and the next region (next-place recommenders; why coarser; region over tracts has little precedent).
%   2.3 Multi-task learning for mobility (MCARNN, iMTL, HMT-GRN; the CSLSL cascade; we predict in parallel, drop next-place).
% Honesty: novelty is the specific combination (check-in level + hierarchical graph + infomax), not a per-visit vector per se.
\section{Background and Related Work}
\label{sec:related}

\subsection{From place embeddings to per-visit embeddings}
\label{sec:related-embeddings}
A place embedding turns a POI into a vector, so that a model can reason about
places by their learned geometry, where similar or nearby places sit close
together. This replaces treating each place as a bare, unrelated index, an
arbitrary ID number that says nothing about what the place is or where it sits.
Deep Graph Infomax (DGI) \cite{velickovic2019dgi} is a general self-supervised
method for learning node representations on graphs. Applied here to a network
of places, it learns such vectors by training them to tell the real place
network, linked by similarity, time, and distance, from a shuffled copy.
Hierarchical Graph Infomax (HGI) \cite{huang2023hgi} adds geographic structure,
organizing the network as place, then region, then city, so the vectors respect
where places sit. Both methods produce one vector per place, so two visits to the
same coffee shop, one at 8\,a.m. and one at 10\,p.m., look identical to the model.
Contextual check-in representations instead give each visit its own vector: CTLE
\cite{lin2021ctle} is the closest example, learning a vector per visit by hiding
parts of a user's check-in sequence and learning to fill them back in. Our
representation, Check2HGI, also works at the check-in level, but it gets there
differently. It keeps the hierarchical place-to-region-to-city network and trains
it with the same infomax objective, now extended one level deeper, from individual
places down to individual check-ins, a fourth level beneath place, region, and
city (Fig.~\ref{fig:dataflow}). It does not switch to a sequence model, as CTLE
does. In short, earlier place embeddings (DGI, HGI) changed \emph{which} features
a place vector encodes; CTLE and we change \emph{how often} a vector is produced,
once per place or once per visit.

The novelty is this specific combination: per-visit context inside a
hierarchical graph-infomax representation. We compare against CTLE directly
to show that the combination, not per-visit context on its own, is the source of
the gain.

\subsection{Predicting the next category and the next region}
\label{sec:related-tasks}
A large body of work predicts the next place a user will visit, the exact POI,
with recurrent and attention models such as ST-RNN \cite{liu2016strnn},
DeepMove \cite{feng2018deepmove}, Flashback \cite{yang2020flashback}, STAN
\cite{luo2021stan}, and GETNext \cite{yang2022getnext}. In contrast, we target two properties of the next visit, its category and its
region, rather than the exact place. These targets are not trivial: the region
alone spans hundreds to several thousand classes. We choose them because they are
what a mobility-aware service can act on, not to make the task easier. The category
task itself follows our earlier line of work \cite{silva2025mtlnet}. The field
increasingly models several granularities at once, predicting category-level and
region-level sequences alongside the place sequence; in that work, however,
category and region are auxiliary signals that help a headline next-place task
(SGRec \cite{li2021sgrec}, MCMG \cite{sun2024mcmg}, HMT-GRN \cite{lim2022hmtgrn}).
We study the pair as the object itself. To our knowledge, fine-grained region as a
co-equal end target, rather than an auxiliary coarse cell, is underexplored:
HMT-GRN, for instance, predicts a coarse geohash cell only as an aid to its
next-place search. We therefore define our region unit carefully when we state the
tasks.

\subsection{Multi-task learning for mobility}
\label{sec:related-mtl}
Multi-task models for mobility have paired location prediction with related
signals for some time. MCARNN \cite{Liao2018} jointly predicts activity and
location, and iMTL \cite{Zhang2020} couples them in a shared, interactive
framework built for sparse check-ins. The closest alternative to our setting is
the cascade. CSLSL \cite{huang2024cslsl} predicts in a chain (when, then what,
then where), with location as the headline output and category as an
instrumental step along the way; CatDM \cite{yu2020catdm} likewise uses category
instrumentally, to filter candidate places. We differ in two ways. We predict
category and region in parallel, as co-equal end targets in one model with a
single forward pass, and we drop next-place entirely, so neither task is
instrumental to a third. On the optimization side we are deliberately
conservative: hard parameter sharing, one shared stack of layers for both tasks, is standard practice
\cite{caruana1997multitask}, and our use of it is not itself the contribution.
Rather than propose yet another gradient-balancing method (PCGrad \cite{yu2020pcgrad},
GradNorm \cite{chen2018gradnorm}, Nash-MTL \cite{navon2022nashmtl}), we ask
where sharing helps and where it costs, and we give a clear, measured account,
consistent with reports that such methods rarely improve on a well-tuned fixed
weighting at two tasks \cite{xin2022domtl, kurin2022defense}. We confirm this on
our own two tasks: across the gradient-balancing methods we tried, including the
three named above, none improved on a tuned fixed task weighting in our model.
The reason is visible in the gradients themselves: the next-category and
next-region updates barely correlate on the shared layers (a near-zero
correlation, about $0.001$, throughout training), so the two tasks neither pull
against each other nor reinforce each other there, and a balancer has no conflict
to resolve. This is consistent with the mechanism we report in
Section~\ref{sec:results-part2}: because the tasks do not compete on the shared
layers, the category gain comes from a stronger shared trunk rather than from the
region task teaching the category one. We report this as our finding for this
pair of tasks, not as a general rule. The novelty here is empirical, not
architectural.
