% Section 3: Problem and tasks (about 0.4 page). Plan: PAPER_PLAN 4 / §3.
% Check-in sequences; windows of nine visits; predict two properties of the next visit:
%   category (7 classes: Community, Entertainment, Food, Nightlife, Outdoors, Shopping, Travel)
%   region (the census tract; the mahalle for Istanbul; ~1k to ~8.5k classes).
% Mobility-aware motivation right-sized to tract granularity (demand/load anticipation, content staging,
% capacity planning); NOT handover / cell-association. No system claim.
\section{Problem and Tasks}
\label{sec:problem}

We work with check-in sequences. For each user we order their check-ins in
time and form short windows of nine consecutive visits. From each window we
predict two properties of the next visit. The first is its \emph{category},
the kind of place, one of seven fixed labels: Community, Entertainment, Food,
Nightlife, Outdoors, Shopping, and Travel. Istanbul uses these same seven
categories through the Massive-STEPS seven-root mapping, so the category label
set is identical across all datasets. The second is its \emph{region}, the census
tract the place falls in (the \emph{mahalle} for Istanbul). We do not predict the
exact next place; these two properties are easier to learn and, for most uses,
enough. Category is a small, fixed label set. Region is a large one: we frame
next-region as classification, where each candidate census tract is one class,
from about five hundred (Istanbul) to about eight thousand five hundred
(California). The spatial task is thus a fine-grained choice over many candidate
regions, while the semantic task is a choice among a handful of kinds of place.

The motivation is practical, and the two predictions correspond to two kinds
of preparation a mobility-aware service makes. The category says what kind of
place comes next, which indicates the content or service a user will want; the
region says where it is, which indicates where to prepare. With both in hand, a
service can act ahead of regional demand, for example by staging content in the
region a user is heading to, or by planning capacity there before the load
arrives. These examples are scoped to what we actually measure. A census tract is
a neighborhood, not a radio cell (the small coverage area a single base station
serves); even the ten most likely tracts are far too coarse to drive cell
association or handover. We therefore keep the motivation at the regional level:
demand and load anticipation, content staging, and capacity planning. With that framing in place, we study how well one model can
anticipate both the category and the region of the next visit. We do not
build or evaluate such a service, or any network system, here; the
application is the reason the predictions matter, not a result we claim.
