% Section 4: Method (about 1.5 pages). Plan: PAPER_PLAN 4 / §4.
%   4.1 The check-in-level representation (Check2HGI): four-level graph (check-in, place, region, city);
%       infomax objective; one vector per check-in. Fig. \ref{fig:dataflow} (top priority).
%   4.2 The single model: shared trunk + private spatial path; one model, one forward pass, two predictions.
%       Fixed-weight sum, both outputs plain unweighted cross-entropy. Cost about +5 percent (one model vs two).
%       Fig. \ref{fig:model}.
\section{Method}
\label{sec:method}

\subsection{The check-in-level representation}
\label{sec:method-rep}

We want each visit, not each place, to carry its own vector. A standard place
embedding gives every point of interest (POI) one fixed vector, so two visits to
the same caf\'e look identical even when they happen at different times of day,
in different company, or after different trips. We instead describe each
check-in in its own context. Figure~\ref{fig:dataflow} shows the full data flow,
from the raw check-in trail to the two outputs.

We build a graph with four levels: the check-in, the place it records, the
region (a census tract) the place sits in, and the city. Edges tie these levels
together and tie check-ins to one another, encoding category similarity (visits
to similar kinds of place), time (visits close in time), and distance (visits
close in space). This keeps the place-to-region-to-city geography of a
hierarchical graph and adds the check-in as a new bottom level. We train the
graph with an infomax objective, which contrasts real neighborhoods against
shuffled ones, so each vector learns to match its real neighborhood and reject a
shuffled one~\cite{velickovic2019dgi,huang2023hgi}. The objective uses no task label: it
never sees the next category or the next region. From the trained graph we read
out one vector per check-in, and a model then sees a sequence of these per-visit
vectors rather than a sequence of repeated per-place ones.

Each ingredient is individually standard: per-visit context, hierarchical place
graphs, and the infomax objective all appear in prior work. The novelty is their
combination, producing a vector per check-in from inside a
hierarchical-graph-infomax representation, which earlier contextual embeddings
built from sequence models (CTLE) do not provide. We show later that this
combination, not extra supervision, is what makes the category task far easier to
learn.

\subsection{The single multi-task model}
\label{sec:method-model}

We then train one model that reads a window of recent per-visit vectors and
predicts two properties of the next visit at once: its category and its region.
Figure~\ref{fig:model} shows the design. Two input streams pass through private
per-task encoders (a small input network dedicated to each task, with no weights
shared between them) into a shared trunk (the stack of layers both tasks use),
where the two streams exchange information (a cross-attention layer lets each
stream read the other's features), and the
trunk feeds two outputs, one for the category and one for the region. The region
output keeps a private spatial path of its own, a small branch that the category
task does not touch.

The private spatial path is a task-specific branch inside the one model, not a
second model, not a second representation, and not a route that swaps models per
task. The whole system is a single model: one set of shared parameters and one
forward pass produce both predictions. This is the deployment property we care
about, since a service that wants both answers runs a single model once, instead
of two separate dedicated single-task models.

The training loss is a fixed-weight sum of the two outputs, and both outputs use
plain unweighted cross-entropy. The two tasks pull in opposite directions on this
choice: the region metric, Acc@10, counts every test visit once, so an unweighted
loss matches it, whereas the category metric, macro-F1, counts every class
equally, so one might expect a class-weighted loss to help. We tested
class-weighting on both heads and it did not help, lowering region accuracy and
also lowering category macro-F1 rather than raising it, so we keep plain
unweighted cross-entropy on both and let the equal-weight sum balance the two
tasks. This is ordinary hard parameter sharing~\cite{caruana1997multitask}, kept
deliberately plain so that any improvement of the joint model over the dedicated
single-task models comes from the shared representation, not from a tuned
weighting scheme.

The cost of serving both tasks this way is modest. The joint model carries both
task heads, so it is larger than a single dedicated model, but it is still
substantially cheaper to serve than the two separate dedicated models the usual
setup would deploy, so two answers come at well under the price of two.
