% Section 5: Experimental Setup (about 1.1 pages). Plan: PAPER_PLAN 4 / §5.
%   5.1 Data -> Table~\ref{tab:datasets}. Five Gowalla states + Istanbul (Massive-STEPS). Seven categories.
%   5.2 Windows, splitting, integrity of the representation (overlapping windows; user-split 5-fold CV;
%       no-leakage argument; per-fold train-only region-transition prior).
%   5.3 Metrics, superiority vs non-inferiority (macro-F1 category; Acc@10 region; paired Wilcoxon for beats;
%       TOST at a two-point margin for matches, justified a-priori with a deployment-grounded rationale + TOST power).
%   5.4 Baselines (POI-RGNN + Markov-9-cat; ReHDM + STAN-on-our-representation; CTLE + feature-concat (FL); CSLSL cascade + HMT-GRN).
\section{Experimental Setup}
\label{sec:setup}

\subsection{Data}
\label{sec:setup-data}
We evaluate on six datasets, summarized in Table~\ref{tab:datasets}. Five come from Gowalla, a location-based
social network, and cover the U.S. states of Alabama, Arizona, Florida, Texas, and California
\cite{cho2011gowalla}; the sixth is the city of Istanbul, drawn from the Massive-STEPS collection
\cite{wongso2025massivesteps}, which gives us a non-U.S. check on the findings. We chose this spread on purpose.
The states run from small to large, from about 114 thousand check-ins and 1,109 regions in Alabama to several
million check-ins and 8,501 regions in California, so we can see whether a result holds as the number of regions
grows. Every dataset uses the same seven place categories: Community, Entertainment, Food, Nightlife, Outdoors,
Shopping, and Travel. The region unit is a census tract for the Gowalla states and a mahalle (a municipal
neighborhood) for Istanbul, and the number of regions ranges from about five hundred to about eight thousand five
hundred.

\subsection{Windows, splitting, and the integrity of the representation}
\label{sec:setup-windows}
\emph{Windows.} For each user with at least ten visits we sort the check-ins in time and form overlapping windows
of nine visits, one starting at each visit, with the next visit as the target. Overlapping windows give the category
task more examples to learn from. Because the windows overlap, many of a user's windows end on the same final visit,
over-representing that one target; we keep a single window ending on each user's last visit and drop the duplicates.
The kept window is a full-context example, not padding.

\emph{Splitting.} We split by user with stratified five-fold cross-validation, so all of a user's windows
fall in the same fold. Overlapping windows therefore cannot leak across the split, because a test user's visits
never appear in training. The split is stratified on the next-category label, which preserves the class proportions
across folds, and this matters because the seven-class category task is imbalanced: Food is the majority class in
every dataset, from about 25 percent of visits in Florida to 34 percent in Alabama.

\emph{Integrity of the representation.} We train the representation once on the whole dataset and then feed it to
both the dedicated single-task models and the joint model, so it is worth being explicit that it carries no
information about the test visits. It does not, for three reasons. First, the representation is trained without any
task label: its objective only contrasts real graph neighborhoods against shuffled ones, and it never sees the
next-category or next-region target, so no label can travel from test to train through it. Second, the only thing
it could carry from the test side is graph structure (which places sit near which, in space, time, and category),
because the graph is built over all places. We measured that exposure directly: for each fold we rebuilt the
representation from only that fold's training users and re-ran both tasks, comparing it against the full-corpus
representation on the same folds. The effect is within fold noise and shows no systematic gain from the wider
exposure: on region the change is $-0.33$ points at Alabama, $+0.01$ at Arizona, and $-0.12$ at Florida, and on
category, measured on the in-coverage visits whose places appear in training (about 67 percent at Alabama to 87
percent at Florida, a place-level proxy, since the representation cannot score a place never seen in training), it is
$+0.29$ at Alabama, $+0.27$ at Arizona, and $+0.00$ at Florida.
% NOTE: numbers from the A4 train-users-only transductivity audit (docs/studies/pre_freeze_gates/A4_RESULTS.md):
% reg AL -0.33 / AZ +0.01 / FL -0.12 (5 folds); cat POI-proxy on in-coverage subset AL +0.29 (66.8%) / AZ +0.27 (71.9%) / FL +0.00 (86.9%).
% Author TODO: extend to CA/TX/Istanbul to widen coverage further (non-blocking; the gate is on null at AL+AZ+FL).
Third, the one component that really passes visit-to-visit information, the region-transition prior used by the
spatial path (a table, built from training data, of how often visits move from one region to the next, used to bias
the region scores), is built per fold from training data only, seed by seed; an earlier version that used the whole
dataset inflated region accuracy by 13 to 27 points across states, so we now build it per fold. Every learned baseline
representation is pre-trained the same way, so all inputs are held to the same standard. The one residual we cannot
fully measure is visits to places never seen in training: the representation is trained having seen all places, so it
cannot score a place absent from training. On the visits we can measure, the large majority, the audit finds no
inflation, and a planned training-only variant is meant to close the remaining gap.

\subsection{Metrics, superiority versus non-inferiority}
\label{sec:setup-metrics}
For the category task we report macro-averaged F1 (macro-F1), which averages the per-class F1 so that each of the
seven categories counts equally, including the rare ones; its reference point is the majority-class floor, the
macro-F1 of always predicting the single most common category. For the region task we report accuracy at ten
(Acc@10), the fraction of test visits whose true region appears among the model's ten highest-scoring guesses; its
comparison anchor is the dedicated single-task model.

We make two kinds of comparison and test each one appropriately. Where the joint model is meant to outperform, we test
\emph{superiority} with a paired Wilcoxon signed-rank test over the folds. Where the joint model is meant only to
stay even, we test \emph{non-inferiority}, that it is no worse than the dedicated model by more than a two-point
margin, with a two-one-sided-tests procedure. We fix the two-point margin in advance and on deployment
grounds, before looking at whether any claim survives it. A mobility-aware service acts on which region will be
busy, not on a single rank position: it anticipates regional demand, stages content for the right region, or plans
capacity at the census-tract level. A two-point shift in Acc@10 is therefore below the granularity at which such a
service would behave differently. The margin is also large relative to the task: with one thousand to
eight thousand five hundred regions, a random top-ten guess lands the true region under one percent of the time,
so two points spans a wide band of the achievable range. Finally, the equivalence is well powered. The per-fold
region standard deviation is small (0.16 to 0.37 points), which gives a power near 1.0 to reject a true two-point
gap, so a non-inferiority verdict reflects a real match rather than a noisy test. Which cells the joint model
outperforms in and which it matches is a result, reported in Section~\ref{sec:results}, not here.

\subsection{Baselines}
\label{sec:setup-baselines}
We compare against baselines in three roles, kept separate so each answers its own question. The first role is the
state of the art for each task, on our data and folds. For next-category this is POI-RGNN \cite{capanema2023poirgnn},
run as a faithful author implementation, and a simple "what usually follows what" Markov baseline over the nine
recent categories (Markov-9). For next-region this is HMT-GRN \cite{lim2022hmtgrn}, our primary region-native
comparison, predicting the region from its own end-to-end recurrent model on the same data, seed, and folds; we run
the HMT-GRN-style trunk and its region-transition prior, and drop its graph module and hierarchical beam search,
which exist to prune a next-place head we do not predict (so the HMT-GRN comparison is a region-native model, not a
component-complete reproduction). Alongside it we run a faithful STAN \cite{luo2021stan}, trained from raw with its
own embeddings and its own sequence construction, and a ReHDM \cite{li2025rehdm} reference reported under that
method's own published protocol rather than as a matched cell. We never feed STAN our representation, because a
representation-fed variant would not be a faithful baseline; such a variant is competitive only at the smallest
state, and we treat it as a direction for future work, not a baseline. The
second role is a representation control, run on Florida, to attribute the category gain to our specific design and
not to contextualization in general or to extra features: CTLE \cite{lin2021ctle}, the closest prior contextual
check-in embedding, presented fairly in both its end-to-end and frozen forms, and a feature-concat control that
appends raw per-visit features to a standard place embedding under the same model. The third role is a multi-task
comparator: the CSLSL cascade \cite{huang2024cslsl}, which predicts in a chain rather than in parallel, so we can
contrast our one-forward-pass joint model against the dominant alternative multi-task design at equal cost. The
dedicated single-task models are the comparison anchors for the joint model throughout, and the standard
place-level embedding \cite{huang2023hgi} is the place-level comparison that isolates what the per-visit
representation adds.
