% Section 6: Results (about 1.5 pages). Plan: PAPER_PLAN 4 / §6. Each result gets a "read this as" lead.
%   6.1 The representation makes the category task learnable (Part 1) -> Table~\ref{tab:substrate}, Fig.~\ref{fig:embquality}.
%   6.2 One model, two tasks (Part 2) -> Table~\ref{tab:results}, Fig.~\ref{fig:deltas}.
%       Category beats everywhere (+4.68..+7.69); region beats at large states (FL/TX/CA), matches at small (AL/AZ/Istanbul).
%       CSLSL cascade ties at equal cost (a defense). All cells n=5 (seed 0) provisional.
%   6.3 External validity (Istanbul): replicates (category beats ~+6.7; region matches ~-0.5); report as gap-to-ceiling / lift.
\section{Results}
\label{sec:results}

\subsection{The representation makes the category task learnable}
\label{sec:results-part1}
Read this as: describing each visit in its own context, rather than each
place once, is what makes the next-category task learnable. Table~\ref{tab:substrate}
compares our check-in-level representation against a standard place embedding
(HGI~\cite{huang2023hgi}) on next-category macro-F1, both fed to the
same dedicated model under the windowing used throughout the paper. This is a
controlled, like-for-like comparison: the target, the single-task head, and the
folds are identical across the two columns, and only the input representation
changes (a vector per visit versus a vector per place), so the margin isolates the
representation, not a difference in task or model. The check-in-level
representation outperforms the place embedding by a wide and consistent margin at every
state: $+29.31$ at Alabama, $+27.63$ at Arizona, $+39.62$ at Florida, $+37.95$
at California, and $+37.47$ at Texas. The same holds on Istanbul ($+26.64$).
The gains fall in two bands, about $+27$ to $+29$ points at the smaller datasets
(Istanbul, Alabama, Arizona) and about $+37$ to $+40$ at the three large states. In absolute terms the place embedding recovers only about half of
what the per-visit representation reaches. A controlled test attributes most of that gain
to the per-visit context itself: replacing each visit's vector with a
per-place-averaged version of the same representation gives back only part of
the margin. This leaves roughly 64 to 90 percent of the gain (state-dependent) to
the context each visit carries, not to extra training signal.

Figure~\ref{fig:embquality} shows why the representation helps this task in
particular. By category, the per-visit vectors are cleanly grouped. Their
silhouette score by category, a separation measure from $-1$ to $1$ where
higher means the seven labeled groups are tighter and better separated, is about $0.56$, against about
$0.00$ for the place embedding. Their nearest-neighbor category purity, the share of a vector's nearest
neighbors that carry its own category, is about $0.98$, against about $0.78$. The same geometry does not separate regions, which is exactly the
point: the representation improves category separability but carries no spatial
structure, so its benefit is category-only and sets up the joint study in
Section~\ref{sec:results-part2}. A direct comparison with the closest prior
contextual embedding makes the source of the gain concrete. CTLE~\cite{lin2021ctle},
which also describes each visit but learns it with a sequence model rather than a
hierarchical graph, reaches only $29.69$ to $33.45$ macro-F1 at Florida across its
trained variants, under the same windowing and the same single-task head; this is far
below our $75.15$. A feature-concat control,
the place embedding joined with raw per-visit features and fed to the same model,
does not close the gap either, so the category gain comes from the hierarchical
per-visit representation, not from contextualization alone and not from feature
injection.

\subsection{One model, two tasks}
\label{sec:results-part2}
Read this as: one model outperforms a dedicated next-category model at every
state and either outperforms or matches a dedicated next-region model, and its
gain on region grows as the number of regions grows.
To calibrate the two scales: category macro-F1 is taken over seven classes (a
majority-class floor of about $7\%$), and region Acc@10 is taken over hundreds to
thousands of regions, where a random top-ten guess is right at most about two
percent of the time (and well under one percent at the larger region counts).
Table~\ref{tab:results} reports the single joint model against the dedicated
single-task ceilings (we call them ceilings because a jointly trained head is
usually expected to match or fall short of a head trained for that task alone).
Figure~\ref{fig:deltas} plots the signed gains ordered by region count. On category the joint model outperforms the dedicated ceiling at
every state, by $+4.68$ to $+7.69$ macro-F1 (smallest at Florida, largest at
Alabama, and $+6.69$ at Istanbul). On region, measured by Acc@10, the joint model outperforms the dedicated ceiling where there are many
regions: Florida $+0.57$ (4{,}703 regions), Texas $+2.06$ (6{,}553), and
California $+2.18$ (8{,}501), each with all five folds in the joint model's favor.
It stays a non-inferior match (TOST, $\pm2$~pp) where there are few: Alabama
$-0.18$, Arizona $-0.06$, and Istanbul $-0.52$. The region gain increases with the number of regions, rising from
$-0.52$ to $+2.18$ across the six settings, so the joint model helps the spatial
task more, not less, as the number of regions grows. The state with the most
regions has the largest region gain, the opposite of a cost that grows with the
size of the spatial problem. We order by region count because that is the axis of
interest; region count and corpus size co-vary across these datasets, so we read
the trend across the six points rather than as a precise law.

The direction is unanimous: at every state all
five folds favor the joint model on category, a one-sided paired Wilcoxon
signed-rank test at its $n{=}5$ floor ($p{=}0.031$ per state), and the sign is
consistent across all six datasets (a 6 of 6 state-level sign test, one-sided
$p \approx 0.016$). At the three large states the region result likewise favors the
joint model on all five folds each. We treat the state, not the fold, as the unit of replication, since
folds within a state share data and the same trained models. The three
small-state region results are tested equivalences (TOST, $\pm2$~pp): Alabama ($-0.18$; 90\% confidence interval
$-0.46$ to $+0.09$), Arizona ($-0.06$; $-0.41$ to $+0.29$), and Istanbul
($-0.52$; $-0.65$ to $-0.35$); all three intervals sit well inside two points.
These intervals are tight because they are built on the \emph{paired} per-fold
difference, whose standard deviation is only $0.16$ to $0.37$ points (the
per-arm fold standard deviations in Table~\ref{tab:results} are larger because
the two models are highly correlated across folds). The equivalence is therefore well
powered. We do not claim per-cell family-wise-corrected significance at $n{=}5$
(a Holm correction across the six cells does not clear $0.05$ at this sample
size), and we leave a multi-seed confirmation ($n{=}20$) to future work.

A reader used to multi-task learning~\cite{caruana1997multitask} expects the
harder task to pay for the easier one, so it is worth saying where the category
gain comes from. A controlled test isolates the source: we freeze the region
pathway at the start of training so it cannot learn, and therefore cannot teach
the category task, yet the full category lift survives at Alabama, Arizona, and
Florida (within $0.3$ of the joint model and far above the dedicated single-task
model). We therefore read the category gain as a stronger shared trunk, obtained
at no extra deployment cost (one model, one forward pass), rather than the region
task teaching the category one; we report this as a finding, not a hypothesis.
The joint model also stands above every external baseline on both tasks at every
state (Table~\ref{tab:results}): the primary region-native comparison,
HMT-GRN~\cite{lim2022hmtgrn} (for example California $49.61$ versus our $65.66$),
a from-raw STAN~\cite{luo2021stan} and a ReHDM reference~\cite{li2025rehdm} on
region, and POI-RGNN~\cite{capanema2023poirgnn} and a Markov floor on category,
all trail it. Every region model clears a simple Markov transition floor by a
wide margin. Against the
closest published multi-task alternative, a cascade that predicts in a chain
(when, then what, then where)~\cite{huang2024cslsl}, our parallel model reaches
the same combined accuracy at the same parameter and compute cost. The difference
on the joint score is about zero. We read this as a defense of the parallel
design, not a claim that we outperform the cascade: the simpler parallel
structure loses nothing. The Gowalla cells
are seed-0 results over five folds ($n{=}5$, provisional); the Istanbul cells
average four seeds ($n{=}20$).

\subsection{External validity (Istanbul)}
\label{sec:results-external}
Read this as: the finding holds on a non-U.S. city, read as a lift over the
dedicated ceiling rather than as an absolute score. On Istanbul the joint model
outperforms the dedicated category ceiling by $+6.69$ macro-F1 ($53.20$ to $59.89$)
and matches the dedicated region ceiling (TOST, $\pm2$~pp), at $-0.52$ Acc@10 ($74.80$ to $74.28$). The category
headline is the four-seed mean against a single-seed ceiling; the clean seed-0
fold-paired gain is $+6.5$ with all five folds positive, so the result does not
rest on the seed averaging. We report Istanbul as a lift over the dedicated
ceiling, not as an absolute Acc@10, because its region count (520 mahalle) differs
from the Gowalla states. The overlapping-window protocol, the fp32 setup, and the
multi-seed run (four seeds, $n{=}20$) match the Gowalla board, so within Istanbul
the multi-task versus dedicated comparison is like-for-like. The external baselines line
up the same way as on the Gowalla states: on category the joint model is far
above a nine-step Markov floor ($24.55$) and POI-RGNN~\cite{capanema2023poirgnn}
($30.12$), and on region it is above a faithful STAN~\cite{luo2021stan} ($61.86$)
and HMT-GRN~\cite{lim2022hmtgrn} ($60.4$). The picture from the U.S. states
repeats on a different continent and a different region unit: the joint model
outperforms on category and stays within two points on region.
