% Section 7: Discussion and Limitations (about 0.5 page). Plan: PAPER_PLAN 4 / §7.
% One model serves both tasks; shared semantic context lifts category, private spatial path keeps region competitive
% (matches at small region counts, outperforms at large). Limitations: single seed over five folds (provisional);
% small-state region is non-inferior within two points (a match, not a beat); transductive representation
% (planned training-only variant); the mobility-aware service is motivation, not evaluated.
\section{Discussion and Limitations}
\label{sec:discussion}

The clearest reading of our results is a design one: one model is enough.
A single model does both jobs at once. It pairs a shared trunk
that carries the semantic context with a private spatial path that keeps
next-region accuracy from degrading. The shared context lifts the next-category task
sharply over a dedicated model at every state, and the private path keeps the
next-region task competitive: a non-inferior match (TOST, $\pm2$~pp) where there
are few regions, and a clear superiority (paired Wilcoxon) where there are many. The region gain is not flat: it rises with the number of regions
(Figure~\ref{fig:deltas}). The benefit from sharing grows as regions
multiply, rather than fading. Overall, the joint model matches or
outperforms the dedicated single-task model on both tasks at once
(Table~\ref{tab:results}). For a mobility-aware service, this
points to a practical option: one model, one forward pass, can anticipate both what a
user will do next and where, without paying for a second model and without
trading one task off against the other.

A short usage sketch makes the motivation concrete. It remains motivation only,
since we measure no service here. A service could treat the model's top-ranked
next regions as an anticipatory set: a small list of areas worth preparing in
advance. The next category then hints at what to prepare in them.
Turning that sketch into a measured result, with its own service baselines and
costs, is future work, not a claim we make.

Three limits qualify these results. First, the joint numbers come from a single
seed over five folds, so they are provisional. A multi-seed run is the obvious
next step and the precondition for any per-cell significance claim
stronger than the ones we report. Second, our representation is trained once over all places. One
slice of its behavior, visits to places never seen during training, is the single
effect we cannot fully isolate. A planned variant that trains on each fold's
training places only is meant to close that gap. Third, although a mobility-aware service is
our motivation throughout, we do not build or evaluate one; tying these
predictions to a concrete service is the natural next study.

Finally, because our representation is a fixed per-visit vector that is computed
once and left unchanged, it is not tied to this particular model: any downstream
model can consume it. Plugging it into other sequence models, and applying it to
mobility tasks beyond next-category and next-region, are natural directions to
explore.
