\section{Discussion and Limitations}
\label{sec:discussion}

We synthesise Sections~\ref{sec:results} and~\ref{sec:mechanism} into four readings: substrate task-asymmetry, scale observations, limitations, and follow-up directions.

The headline reading is that the MTL picture is dominated by the \emph{substrate's task-asymmetric value}, not cross-task transfer through joint training. Per-visit context is paper-grade significant for next-category at every state ($+14.5$ to $+29$ pp matched-head); on next-region the same substrate ties or marginally trails HGI by $1.6$ to $3.1$ pp under the matched-head \texttt{next\_stan\_flow} ceiling, with TOST $\delta=2$ pp passing at CA and TX. With Check2HGI fixed, the cross-attention MTL backbone adds a small category lift at four of five states (AZ $+1.20$, FL $+1.40$, CA $+1.68$, TX $+1.89$ pp at $p\leq 2\mathrm{e}{-6}$, $n=20$) and is small-significantly negative at AL ($\Delta=-0.78$ pp, $p=0.036$, $n=20$); on next-region it pays a sign-consistent $7$ to $17$ pp cost on Acc@10 at every state ($p\leq 1.9\mathrm{e}{-6}$, $n=20$). The conventional MTL framing where joint training transfers signal to lift both heads does not hold on the harder task: the category lift survives the substrate ablation, and the region cost survives the substrate fix. The honest reattribution is substrate first (task-asymmetric), MTL coupling second (tradeoff-paying).

The reg cost varies in magnitude but not sign: AL, AZ, FL trend downward ($-11.04$, $-12.27$, $-7.34$ pp), CA preserves at $-9.50$ pp, TX breaks monotonicity at $-16.59$ pp. We report descriptively, not as an inferential scaling claim. Trajectory geometry, transition-graph density, and short-horizon Markov coverage are plausible drivers, none directly testable at our state count.

Six limitations apply. The per-visit mechanism is single-state (AL only); the $\sim 72\,\%/\sim 28\,\%$ split is scoped to that state, and a second-state replication is left to follow-up. At FL the next-region task sits in a Markov-saturated Acc@10 regime, evidenced by the Markov-1-region floor at $65.05$ Acc@10 (Table~\ref{tab:external}); the MTL backbone trails this floor on Acc@10 ($63.27$) but is paper-grade positive on $\Delta_m$ MRR ($+2.33\,\%$, $n=25$). The Acc@10 axis is therefore a less informative tradeoff metric at this state and region cardinality, and we report MRR alongside. The drop-in MTL ablation panel ran at FL only; the cost is sign-consistent across the five states, so the structural reading transfers, but a five-state replication is left to follow-up. External baseline coverage is asymmetric: ReHDM~\cite{li2025rehdm} is reported at AL, AZ, FL only, because its dual-level hypergraph collaborator pool grows quadratically with region cardinality and exceeded our compute budget at CA/TX on a single H100. Our POI-RGNN~\cite{capanema2022poirgnn} reproduction enforces user-disjoint folds (the published evaluation used non-user-disjoint folds); the $+27$ to $+29$ pp matched-head Check2HGI minus POI-RGNN gap is a conservative lower bound. Finally, \texttt{StratifiedGroupKFold} with shuffling produces different splits across sklearn versions; paired tests within one environment are unaffected, but absolute leak-magnitude attribution requires single-environment re-runs.

Two directions follow. Asymmetric routing (PLE~\cite{tang2020ple}, Cross-Stitch~\cite{misra2016crossstitch}) frees the region head from shared-backbone interference; whether such routing recovers the MTL-over-STL gap on next-region without sacrificing the category lift is the next experiment. Encoder enrichment is the second axis: Paiva et al.\ (2026), which decomposes the monolithic embedding into spatial, temporal, and categorical sub-encoders, and our substrate response are complementary, and a fused substrate combining per-visit context with explicit spatial and temporal encoders is plausibly the path to a Pareto-positive joint solution. Both are out of scope here.
