\section{Introduction}
\label{sec:intro}

Location-Based Social Networks (LBSNs), such as Gowalla~\cite{cho2011gowalla}, record sequences of geo-tagged user \emph{check-ins}, where each check-in stores when, where, and what kind of place a user visited. In this context, a Point of Interest (POI) is a physical place with semantic meaning, such as a restaurant, a shopping mall, an airport, or a park~\cite{silva2025mtlnet}.

From these traces, two prediction tasks recur in the literature. \textbf{Next-category prediction} forecasts the semantic category of the next visit (e.g.\ \emph{Food}, \emph{Shopping}, \emph{Travel}) and feeds content-aware recommendation and intent inference. \textbf{Next-region prediction} forecasts the next visit's spatial \emph{region} (a coarse geographic cell that may contain many POIs, not an individual POI) and feeds demand forecasting and short-horizon mobility planning.

Because both tasks read the same mobility data, Multi-Task Learning (MTL)~\cite{caruana1997multitask,vandenhende2022mtl} is a natural fit: the standard appeal is that a shared representation lets one task's signal benefit the other and lift both. In practice the two tasks have different natures. Predicting a category is a coarse semantic decision shaped by per-visit context (intent, time of day, what the user did just before); predicting a region is a fine-grained spatial ranking driven by short-horizon transitions and spatial regularities. Forcing one shared representation to serve both can either help or hurt, the well-known risk of \emph{negative transfer}~\cite{vandenhende2022mtl}.

Two recent studies on this exact task pair report the negative outcome. The first applies hard-parameter-sharing MTL on top of a POI-stable graph embedding (one vector per place, learned with DGI~\cite{velickovic2019dgi}) and finds only marginal joint gains, with most differences within standard deviations; it diagnoses a \emph{representation mismatch}, where one shared encoder learns a compromise specialised enough for neither head~\cite{silva2025mtlnet}. The follow-up keeps the same MTL recipe but decomposes the monolithic embedding into independent spatial, temporal and categorical sub-encoders, and recovers substantial category-side gains across three states~\cite{paiva2026courb}. Together they suggest the central factor is the embedding the multi-task model consumes, not the loss-balancing recipe itself.

Both prior responses kept the embedding's \emph{emission rate} fixed (one vector per place) and changed \emph{which} features were encoded. We test an orthogonal axis: how often the embedding emits a vector. POI-stable embeddings such as HGI~\cite{huang2023hgi} emit a single vector per place, so two visits to the same caf\'e at 8:00 and at 22:00 produce identical inputs. A check-in-level embedding instead emits one vector per visit, so the two visits can differ. We hypothesise that this per-visit context is the load-bearing property for the easier head (next-category), and that, once the upstream embedding (the \emph{substrate}, by contrast with the downstream multi-task \emph{backbone}) is fixed at the right granularity, joint training behaves like the classic MTL tradeoff: a small gain on the easier task at the cost of the harder one.

To test this hypothesis, we propose \textbf{Check2HGI}, a check-in-level extension of the hierarchical graph-infomax line, and run a controlled five-state ablation on user-disjoint splits of Gowalla, covering Alabama (AL), Arizona (AZ), Florida (FL), California (CA) and Texas (TX). We compare Check2HGI against per-place HGI under \emph{matched-head single-task ceilings}: the same task-specific head trained alone on each substrate, so any difference between rows is attributable to the substrate rather than to head capacity. The findings are asymmetric across the two tasks. Per-visit context lifts next-category macro-F1 by $+14$ to $+29$ percentage points (pp) at every state; on next-region, per-place HGI ties or marginally exceeds Check2HGI. Joint multi-task training over Check2HGI then adds a small category lift at four of five states and pays a $7$ to $17$ pp cost on next-region top-10 accuracy at every state, the expected MTL tradeoff now made explicit.

The main contributions of this paper are as follows.\footnote{To support reproducibility, the full artefact set (code, fold splits, seeds, per-fold transition priors, and regression tests) is released at \url{https://anonymous.4open.science/r/PoiMtlNet-FE6A/}.}
\begin{itemize}
    \item C0. We propose \emph{Check2HGI}, a check-in-level contextual graph embedding that extends HGI's hierarchical contrastive objective with a fourth emission level (Check-in $\to$ POI $\to$ Region $\to$ City), so that the same place visited twice can yield two distinct vectors.
    \item C1. A controlled five-state matched-head ablation that separates the substrate's contribution from head capacity. Check2HGI lifts single-task category macro-F1 over per-place HGI by $+14$ to $+29$ pp at every state (paired Wilcoxon $p = 0.0312$ each, 5/5 folds positive); on next-region, the same substrate ties or marginally trails per-place HGI. A pooled-vs-canonical counterfactual replicates at Alabama and Arizona, attributing $\sim$72\,\% and $\sim$64\,\% of the category gap to per-visit context.
    \item C2. A direct characterisation of the multi-task tradeoff under the substrate established by C1: with the substrate fixed, joint multi-task training adds a small category lift at four of five states and pays a sign-consistent $7$ to $17$ pp cost on next-region top-10 accuracy at every state. Drop-in balancers and a head-side fix do not close the gap, indicating a structural cost of the cross-attention shared backbone interacting with the region head rather than a loss-recipe artefact.
\end{itemize}

Sections~\ref{sec:related}, \ref{sec:method}, and~\ref{sec:setup} cover related work, method, and setup. Section~\ref{sec:results} shows that the substrate is asymmetric across the two tasks: per-visit context carries next-category at every state, while per-place embeddings tie or marginally trail it on next-region. With the substrate fixed, joint multi-task training delivers a small category lift at four of five states and pays the expected region cost. Section~\ref{sec:mechanism} attributes the substrate gain through a per-visit counterfactual, ablates drop-in balancers and a head-side fix, and adds a methodological note on cross-attention loss-side ablations. Sections~\ref{sec:discussion}~and~\ref{sec:conclusion} close.
