\section{Related Work}
\label{sec:related}

Three lines of work bear on our study: graph-based POI embeddings that supply the substrate, multi-task learning balancers that sit on top of any joint architecture, and prior multi-task work on the POI category and next-POI pair. We summarise each line briefly and position our contribution against it; a fourth note on cross-attention multi-task models is deferred to the methodological discussion in Section~\ref{sec:mechanism}.

\subsection{Graph-based POI embeddings}
\label{subsec:related-embeddings}

Substrate choice is the load-bearing axis our study tests, so we trace the graph-based line that produces it. Early POI representations such as POI2Vec~\cite{feng2017poi2vec} learn one vector per place from co-visit statistics, treating the POI as the atomic unit. CATAPE~\cite{rahmani2019catape} extends the idea by injecting category supervision into the embedding objective, but the emission rate stays at one vector per POI. Self-supervised graph contrastive methods then sharpened the representation: Deep Graph Infomax (DGI)~\cite{velickovic2019dgi} maximises mutual information between local node embeddings and a global graph summary, and Hierarchical Graph Infomax (HGI)~\cite{huang2023hgi} adapts the contrast across POI, region, and city graphs to capture multi-scale urban structure. Both DGI and HGI emit \emph{POI-stable} vectors, so the same place visited twice yields the same representation regardless of when or with whom the visit happened. The substrate we use, \emph{Check2HGI}, is a check-in-level extension of HGI's hierarchical contrastive objective: contrastive views are sampled at the granularity of a single check-in rather than a single POI, and the visit's temporal and co-visit context perturbs the view, so the same POI visited twice can yield two distinct vectors. This per-visit emission rate is the property our substrate axis tests; the recipe is described in supplementary material and in our anonymous code release.

\subsection{Multi-task learning balancers}
\label{subsec:related-mtl}

A second body of work studies how to combine task losses or task gradients once the architecture is fixed. The line of gradient-balancing methods includes GradNorm~\cite{chen2018gradnorm}, which rescales per-task gradients to match a target relative training rate, PCGrad~\cite{yu2020pcgrad}, which projects each task's gradient onto the orthogonal complement of any conflicting task, CAGrad~\cite{liu2021cagrad}, which constrains the joint update to descend on every task's loss within a trust region, and NashMTL~\cite{navon2022nashmtl}, which solves a small bargaining game per step to choose the update direction. More recent proposals continue along the same axis: FAMO~\cite{liu2023famo} adapts loss weights using per-task progress estimates, and Aligned-MTL~\cite{senushkin2023aligned} aligns gradient directions through an independent-component decomposition. The classic survey of multi-task learning for dense prediction~\cite{vandenhende2022mtl} aggregates these methods and reports that no balancer dominates across task pairs; the textbook tradeoff identified by Caruana~\cite{caruana1997multitask} and quantified by Maninis et al.~\cite{maninis2019attentive} through the $\Delta_{m}$ joint score remains the operating regime. Our setup uses a fixed static-weight aggregation with $\lambda_{\text{cat}} = 0.75$. We do not propose a new balancer, and we ablate against FAMO and Aligned-MTL in Section~\ref{sec:mechanism} to check whether a drop-in balancer recovers the next-region cost we will report.

\subsection{Prior POI multi-task work}
\label{subsec:related-poi-mtl}

A third line is concept-aligned with our task pair. HMT-GRN~\cite{lim2022hmtgrn} jointly predicts next-POI and next-region through a hierarchical graph recurrent network, GETNext~\cite{yang2022getnext} combines a transformer with an additive log-transition prior over a trajectory flow map, and the human-mobility representation model~\cite{chen2020hmrm} jointly models attribute and trajectory signals through shared encoders. STAN~\cite{luo2021stan} addresses the next-location subproblem with spatio-temporal self-attention and is the backbone we adapt for our region head; we borrow GETNext's additive $\alpha \cdot \log T$ prior pattern but do not include its friendship or check-in graph priors, so our region head is not a faithful GETNext reproduction. ReHDM~\cite{li2025rehdm} extends the hypergraph line with a region-aware dual-level model and serves as our concept-aligned external next-region baseline. Two recent works on the precise category and next-POI pairing are closer still. A first study trained a hard-parameter-sharing multi-task framework over POI-stable graph embeddings (DGI), comparing against single-task baselines such as HMRM~\cite{chen2020hmrm} and MHA+PE~\cite{zeng2019mhape}, and reported only marginal joint gains, with most differences within standard deviations; the diagnosis pointed at representation mismatch, where a single shared encoder learns a compromise specialised enough for neither head~\cite{silva2025mtlnet}. A follow-up tested an embedding-side response by decomposing the monolithic graph embedding into independent spatial, temporal, and categorical sub-encoders, and recovered substantial category-side gains across three states, supporting the reading that the embedding choice was the load-bearing factor~\cite{paiva2026courb}. Both responses kept the embedding's per-POI emission rate fixed and varied the \emph{what} axis (which features to encode); our study varies the \emph{granularity} axis instead.

Our work re-examines a default reading of multi-task learning for POI category and next-POI prediction: that joint training transfers signal between heads to lift both jointly. With the substrate held fixed at the right granularity, we find that joint cross-attention training delivers a small additional category lift at four of five Gowalla~\cite{cho2011gowalla} state splits and pays a sign-consistent cost on next-region at every state, the textbook tradeoff. Our contribution is empirical and methodological. We do not propose a new balancer, head, or attention variant; we use a controlled five-state ablation on user-disjoint folds to reattribute the joint result, separating the substrate's contribution from the architecture's.
